---
title: "Sliced-04"
author: "JJayes"
date: "23/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Core tidyverse
library(tidyverse)
library(scales)
library(lubridate)
theme_set(theme_light())

# Tidy Models
library(tidymodels)
library(textrecipes)
library(stacks)
doParallel::registerDoParallel(cores = 4)

```

Set up the datasets.

```{r}
# RMSE for linear (or roc_auc, etc, but better to pick one)
mset <- metric_set(rmse)
# Set up to inspect model outputs, or to stack model candidates
grid_control <- control_grid(save_pred = TRUE,
                             save_workflow = TRUE,
                             extract = extract_model)
```

```{r}
folder <- "~/Recon/sliced/Sliced-04/"
dataset <- read_csv(paste0(folder, "train.csv"))
holdout <- read_csv(paste0(folder, "test.csv"))
sample <- read_csv(paste0(folder, "sample_submission.csv"))
# What are we predicting?
colnames(sample)
set.seed(2021)
spl <- initial_split(dataset, .prop = .75)
train <- training(spl)
test <- testing(spl)
train_fold <- train %>%
  vfold_cv(5)
```

### EDA

What is the outcome we want to predict?

```{r}
train %>% count(rain_tomorrow, sort = T)
```

Whether it will rain tomorrow. We have a class imbalance. Roughly 22 percent of the sample has rain tomorrow.

We can use the themis package to smote upsample the days of rain tomorrow.

What other information do we have?

```{r}
train %>% skimr::skim()
```


```{r}
train %>% 
    count(location, sort = T) %>% 
    tail()

train %>% count(rainfall, sort = T)

train %>% 
    ggplot(aes(rainfall, fill = rain_tomorrow)) + 
    geom_density()

```

Lots of rain today correlated with rainfall tomorrow. Makes sense.

```{r}
train %>% 
    count(rain_today, rain_tomorrow, sort = T)

train %>% 
    filter(!is.na(rain_today)) %>% 
    count(rain_today, rain_tomorrow, sort = T) %>% 
    ggplot(aes(rain_today, rain_tomorrow, fill = n)) +
    geom_tile()

train %>% ggplot(aes(rainfall, rain_tomorrow)) +
    geom_point() +
    geom_smooth()

```

What's the deal with wind? Surely location specific?

```{r}
train %>% 
    count(wind_gust_dir, sort = T)

train %>% 
    count(wind_gust_dir, rain_tomorrow, sort = T) %>% 
    ggplot(aes(n, wind_gust_dir, fill = factor(rain_tomorrow))) +
    geom_col(position = "dodge") 

train %>% 
    count(wind_gust_speed, rain_tomorrow, sort = T) %>% 
    ggplot(aes(wind_gust_speed, n, colour = factor(rain_tomorrow))) +
    geom_point() 

```

What's the deal with temperature?

```{r}
train %>% 
    ggplot(aes(min_temp, rain_tomorrow)) +
    geom_point() +
    geom_smooth()

train %>% 
    ggplot(aes(max_temp, rain_tomorrow)) +
    geom_point() +
    geom_smooth()
```

That's super surprising! Min temp is increasing in probability of rain, but max temp is decreasing!

```{r}
train %>% 
    ggplot(aes(max_temp, rain_tomorrow)) +
    geom_point() +
    geom_smooth() +
    facet_wrap(~ rain_today)

```

We can see that if there is a low temperature today and a low max_temp today and rain today, there is a super high likelihood of rain tomorrow.

What's the deal with seasonality?

```{r}
train %>% 
    select(date)

train %>% 
    mutate(week = week(date)) %>% 
    ggplot(aes(week, rain_tomorrow)) +
    geom_point() +
    geom_smooth()

train %>% 
    filter(!is.na(rain_today)) %>% 
    mutate(week = week(date)) %>% 
    ggplot(aes(week, rain_tomorrow)) +
    geom_point() +
    geom_smooth() +
    facet_wrap( ~ rain_today)

```

There is winter rain, with higher likelihood of rain tomorrow if there is rain today.

What do we do with evaporation and sunshine? I'm not really sure

```{r}
train %>% 
    count(sunshine, rain_tomorrow)

train %>% 
    count(evaporation, rain_tomorrow)
    
```


### Make a model

```{r}
library(themis)

rf_rec <- recipe(rain_tomorrow ~ ., data = train) %>% 
    update_role(id, "id") %>% 
    step_mutate(rain_tomorrow = factor(case_when(
        
        rain_tomorrow > 0 ~ "rain",
        TRUE ~ "no rain"
        
    ))) %>% 
    step_date(date, features = c("month", "week")) %>%
    step_rm(date, evaporation, sunshine) %>%
    step_impute_median(all_numeric_predictors()) %>%
    step_impute_knn(all_nominal_predictors()) %>% 
    step_other(location, wind_gust_dir, wind_gust_speed) %>%
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors()) %>% 
    step_smote(rain_tomorrow)

rf_rec %>% prep() %>% juice()
    
```

### Random forest model

```{r}
# recipe
ranger_rec <- rf_rec %>% 
    step_mutate(rain_tomorrow = as.numeric(rain_tomorrow))

# model specification
ranger_spec <- 
  rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
  set_mode("regression") %>% 
  set_engine("ranger") 

# model workflow
ranger_workflow <- 
  workflow() %>% 
  add_recipe(ranger_rec) %>% 
  add_model(ranger_spec)

# hyper parameters
params <- parameters(ranger_spec) %>% 
    update(mtry = finalize(mtry(), x = train %>% select(-rain_tomorrow)))

# grid
ranger_grid <- grid_regular(params, levels = 5)

```

```{r}
set.seed(79912)
ranger_tune <- tune_grid(ranger_workflow, 
                resamples = train_fold,
                control = control_grid(save_pred = TRUE),
                grid = ranger_grid)

ranger_tune %>% collect_metrics()

ranger_tune %>% select_best()

ranger_best <- ranger_tune %>% select_best()

ranger_pred <- ranger_tune %>% 
  collect_predictions(parameters = ranger_best) %>% 
  mutate(model = "Ranger")

ranger_pred %>% 
    ggplot(aes(.pred, profit)) +
    geom_point() +
    geom_abline()

library(vip)
# testing
ranger_tune %>% pull_workflow_fit() %>% vip()

```

