---
title: "Sliced-07"
author: "JJayes"
date: "14/07/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidymodels)
library(scales)

theme_set(theme_light())
```

### Purpose

Doing sliced 07 predicting churn

### Reading in data

```{r}
education_levels <- c("Unknown", "Uneducated", "High School", "College", "Graduate", "Post-Graduate", "Doctorate")

income_categories <- c("Unknown", "Less than $40K", "$40K - $60K", "$60K - $80K", "$80K - $120K", "$120K +")

df <- read.csv("train.csv") %>% as_tibble() %>% rename(churned = attrition_flag) %>% 
  mutate(churned = if_else(churned == 1, "yes", "no"),
         education_level = fct_relevel(education_level, education_levels),
         income_category = fct_relevel(income_category, income_categories))

test_data <- read.csv("test.csv") %>% as_tibble() %>% 
  mutate(education_level = fct_relevel(education_level, education_levels),
         income_category = fct_relevel(income_category, income_categories))

ss <- read.csv("sample_submission.csv")

```

### What are we predicting?

```{r}
colnames(ss)
```

Attrition flag

### Spend the data budget

```{r}
spl <- initial_split(df, strata = churned)

train <- training(spl)
test <- testing(spl)
folds <- vfold_cv(train, v = 5)
```

### Modelling prep
Creating a metric set - we are being evaluated on logloss

```{r}
mset <- metric_set(mn_log_loss, accuracy, specificity)

grid_control <- control_grid(save_pred = TRUE,
                             save_workflow = TRUE,
                             extract = extract_model)

```

### parallel backend

```{r}
library(doParallel)

cl <- makePSOCKcluster(8)
registerDoParallel(cl)

clusterEvalQ(cl, {library(tidymodels)})
```


## EDA

```{r}
train %>% count(churned)
```

Highly unbalanced data set. Maybe use an auto encoder??

```{r}
train %>% skimr::skim()

train %>% count(education_level)
train %>% count(income_category)

train %>% count(total_relationship_count)
```


```{r}
library(ggridges)
library(wesanderson)

train %>% 
    select(-id, -gender, -education_level, -income_category) %>% 
    gather(variable, value, -churned) %>% 
    ggplot(aes(y = factor(variable),
               fill = factor(churned),
               x = percent_rank(value))) +
    geom_density_ridges(alpha = .7) +
    scale_fill_manual(values = wes_palette("Darjeeling1")) +
  labs(x = "Percentile of predictor",
       y = NULL,
       fill = "Churned")

```

### Summarize churn

```{r}
summarise_churn <- function(tbl){
  
  tbl %>% 
    summarise(n = n(),
              n_churned = sum(churned == "yes"),
              pct_churned = n_churned / n,
              low = qbeta(.025, n_churned + .5, n - n_churned + .5),
              high = qbeta(.975, n_churned + .5, n - n_churned + .5)) %>% 
    arrange(desc(n))
  
}

train %>% group_by(gender) %>% summarise_churn()
```


```{r}
train %>% 
  group_by(gender) %>% 
  summarise_churn() %>% 
  ggplot(aes(pct_churned, gender, fill = gender)) +
  geom_col(show.legend = F) +
  geom_errorbarh(aes(xmin = low, xmax = high), height = .5) +
  scale_x_continuous(labels = percent) +
  labs(x = "Percent churned",
       y = "Gender") +
  scale_fill_manual(values = wes_palette("Darjeeling2"))

train %>% 
  group_by(education_level) %>% 
  summarise_churn() %>% 
  ggplot(aes(pct_churned, education_level, fill = education_level)) +
  geom_col(show.legend = F) +
  geom_errorbarh(aes(xmin = low, xmax = high), height = .5) +
  scale_x_continuous(labels = percent) +
  labs(x = "Percent churned",
       y = "Gender") +
  scale_fill_brewer(palette = "Paired")

```



### Penalized linear regression

```{r}
library(themis)

glmnet_recipe <- 
  recipe(formula = churned ~ ., data = train) %>% 
    step_mutate(churned = factor(churned)) %>% 
  step_factor2string(gender, education_level, income_category) %>% 
  step_novel(all_nominal_predictors()) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_nzv(all_predictors()) %>% 
  step_normalize(all_numeric_predictors()) %>% 
    step_smote(churned)

glmnet_spec <- 
  logistic_reg(penalty = tune(), mixture = 1) %>% 
  set_mode("classification") %>% 
  set_engine("glmnet") 

glmnet_workflow <- 
  workflow() %>% 
  add_recipe(glmnet_recipe) %>% 
  add_model(glmnet_spec) 

glmnet_grid <- tidyr::crossing(penalty = 10^seq(-6, -1, length.out = 20)) 

glmnet_tune <- 
  tune_grid(glmnet_workflow, 
            metrics = mset,
            resamples = folds,
            grid = glmnet_grid)
```

What does it look like?

```{r}
glmnet_tune %>% autoplot()
```

### xgboost model

```{r}
usemodels::use_xgboost(formula = churned ~ ., data = train)
```

We want to do an xgboost model and add in the ones that are numeric, and make the categorical ones ordinal.

```{r}
library(themis)

xgboost_recipe <- 
  recipe(formula = churned ~ ., data = train) %>% 
  update_role(id, new_role = "id") %>% 
  step_mutate(income_category = as.integer(income_category)) %>% 
  step_mutate(education_level = as.integer(education_level)) %>% 
  step_novel(all_nominal_predictors()) %>% 
  step_dummy(all_nominal_predictors()) %>% 
  step_nzv(all_predictors()) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_smote(churned)

xgboost_recipe %>% prep() %>% juice()

xgboost_spec <- 
  boost_tree(trees = tune(), mtry = tune(), learn_rate = tune()) %>% 
  set_mode("classification") %>% 
  set_engine("xgboost") 

xgboost_workflow <- 
  workflow() %>% 
  add_recipe(xgboost_recipe) %>% 
  add_model(xgboost_spec) 

xgboost_grid <- crossing(trees = seq(500, 1100, 50),
         mtry = c(4, 6, 8, 10),
         learn_rate = c(.01, .02))

set.seed(2021)
xgboost_tune <-
  tune_grid(xgboost_workflow, 
            resamples = folds, 
            metrics = mset,
            control = grid_control,
            grid = xgboost_grid)
```

What does it look like?

```{r}
xgboost_tune %>% autoplot()

xgboost_tune %>% collect_metrics() %>% 
  filter(.metric == "mn_log_loss") %>% arrange(mean)
```

With step smote mean log loss is 0.0950
Without step smote mean log loss is 0.0897


Making a variable importance plot

```{r}
library(vip)

xg_fit <- xgboost_workflow %>% 
  finalize_workflow(select_best(xgboost_tune, metric = "mn_log_loss")) %>% 
  fit(train)

fit <- xg_fit %>% pull_workflow_fit()


xg_fit %>% 
  augment(test), type.predict = "prob") %>% 
  mn_log_loss(.pred)
```


# Following on from david robinson

QQ: How to deal with ordinal categories? Just make them numeric?

Want to make a function called summarize attrition that gives mean attrition for each slice of data.

```{r}

```

